### 2014-10-06 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits

On-scene photographs and post-incident reports were used to estimate the type of fuel, fire size, and ventilation openings on the structure. Based on these sources of information, the FDS model included three source fires: 1)~an initial couch fire in the basement, 2)~a flashover fire that involved additional furniture items in the basement, and 3) a fire that occurred on the balcony located on the rear exterior side of the basement.

@@

The HRRs for the three primary source fires were prescribed in FDS as follows.

@@

\\ For specific information regarding ventilation areas used in the FDS model, refer to Table~\ref{tab:ventilation_timeline}.

>>>>

On-scene photographs and post-incident reports were used to estimate the type of fuel, fire size, and ventilation openings on the structure. Based on these sources of information, the simulation included three source fires: 1)~an initial couch fire in the basement, 2)~a flashover fire that involved additional furniture items in the basement, and 3) a fire that occurred on the balcony located on the rear exterior side of the basement.

@@

The HRRs for the three primary source fires were prescribed in the simulation as follows.

@@

\\ For specific information regarding ventilation areas used in the simulation, refer to Table~\ref{tab:ventilation_timeline}.
